TBD

### 2016-09-28 paper.tex
LINCAL partial
LINCAL again

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\subsection{LINCAL}
\begin{equation}
c_{ij} = y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
\end{equation}

>>>>

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\subsection{LINCAL}
Assume that $\eta_i,\eta_j,\widetilde{\eta}_{\phi_{ij}},\varphi_i,\varphi_j$ and $\widetilde{\varphi}_{\phi_{ij}}$ are real valued variables.
Substituting $g_i$ with $e^{\eta_i - i \varphi_i}$, $g_j$ with $e^{\eta_j - i \varphi_j}$ and $y_{\phi_{ij}}$ with $e^{\eta_{\widetilde{\phi}_{ij}}- i \widetilde{\varphi}_{\phi_{ij}}}$ in Eq.~\eqref{eq:vis_red} results in  
\begin{equation}
\label{eq:lincal}
d_{ij} =  e^{\eta_i - i \varphi_i} e^{\widetilde{\eta}_{\phi_{ij}}- i \widetilde{\varphi}_{\phi_{ij}}} e^{\eta_j + i \varphi_j} + n_{ij}.
\end{equation}

A possible approach one can use to solve the unknowns in Eq.~\eqref{eq:lincal} is to write down the Taylor expansion of the first term of the right hand side of Eq.~\eqref{eq:lincal} around some 
initial fiducial guess of $\eta_i,\eta_j,\widetilde{\eta}_{\phi_{ij}},\varphi_i,\varphi_j$ and $\widetilde{\varphi}_{\phi_{ij}}$, which we denote with 
$\eta_i^0,\eta_j^0,\widetilde{\eta}_{\phi_{ij}}^0,\varphi_i^0,\varphi_j^0$ and $\widetilde{\varphi}_{\phi_{ij}}^0$, and then to solve the perturbations from this 
initial guess that minimize the difference between the right and left hand side of Eq.~\eqref{eq:lincal}. Once the perturbation values 
have been computed it is trivial to obtain an estimate of $g_i$, $g_j$ and $y_{\phi_{ij}}$.

If we Taylor expand the first term on the right hand side of Eq.~\eqref{eq:lincal} around a fiducial initial guess we obtain
\begin{equation}
\label{eq:taylor_expansion}
d_{ij} = v_{ij}^0[1+\Delta \eta_i + \Delta \eta_j + i \varphi_i - i \Delta \varphi_j + \Delta \widetilde{\eta}_{\phi_{ij}} + i\Delta \widetilde{\eta}_{\phi_{ij}}] + n_{ij}, 
\end{equation}
where
\begin{equation}
v_{ij}^0 = e^{\eta_i^0 - i \varphi_i^0} e^{\widetilde{\eta}_{\phi_{ij}}^0 - i \widetilde{\varphi}_{\phi_{ij}}^0} e^{\eta_j^0 + i \varphi_j^0}, 
\end{equation}
and $\eta_i^0,\eta_j^0,\widetilde{\eta}_{\phi_{ij}}^0,\varphi_i^0,\varphi_j^0$ and $\widetilde{\varphi}_{\phi_{ij}}^0$ respectively denote the initial guess for $\eta_i,\eta_j,\widetilde{\eta}_{\phi_{ij}},\varphi_i,\varphi_j$ and $\widetilde{\varphi}_{\phi_{ij}}$.
Eq.~\eqref{eq:taylor_expansion} can be used to construct the following linear system
\begin{equation}
\breve{\br} = \bJ\Delta\widetilde{\bz}, 
\end{equation}
where 
\begin{equation}
\breve{\br} = [d_{ij}-v_{ij}^0] \big \} ~ [ij] = 1\cdots 2B, 
\end{equation}
\begin{equation}
\label{eq:jac_lincal}
\bJ = \begin{bmatrix}
      \bN & \bM\\
      \conj{\bN} & \conj{\bM}
      \end{bmatrix}
\end{equation}
and
\begin{equation}
\Delta\widetilde{\bz} = 
\begin{bmatrix}
\Delta \eta_i \\
\Delta \varphi_j \\
\Delta \widetilde{\eta}_k \\
\Delta \widetilde{\varphi}_l \\
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\eta_i}{i = 1\cdots N}\\
\coolrightbrace{\eta_i}{j = 1\cdots N}\\
\coolrightbrace{\eta_i}{k = 1\cdots L}\\
\coolrightbrace{\eta_i}{l = 1 \cdots L}
\end{matrix}.
\end{equation}

In Eq.~\eqref{eq:jac_lincal}

\begin{eqnarray}
\bN &=& 
\begin{bmatrix}
\coolover{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,N}}{\frac{\partial v_{pq}}{\partial \eta_j}} & \coolover{\!\!\!\!{\scriptstyle k=1,\ldots,N}}{~\frac{\partial v_{pq}}{\partial \varphi_k}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
&=& \begin{bmatrix}
\coolunder{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,N}}{n_{j,pq}} & \coolunder{\!\!\!\!{\scriptstyle k=1,\ldots,N}}{(-1)^{\delta_q^k}i n_{k,pq}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
\end{eqnarray}

Moreover,
\begin{equation}
n_{j,pq} = (\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq} 
\end{equation}

fiducial initial guess

The following partial derivatives are now easily computed
